---
title: "607wk3Homework"
author: "Angus Huang"
date: "September 12, 2015"
output: html_document
---
1.Load the raw data in as a data frame
```{r}
library (plyr)
bridge1 <-data.frame (read.csv("https://archive.ics.uci.edu/ml/machine-learning-databases/bridges/bridges.data.version1", header = FALSE))
bridge <-data.frame(read.csv("https://archive.ics.uci.edu/ml/machine-learning-databases/bridges/bridges.data.version2",header=FALSE))
head(bridge)
summary(bridge)

```
2. Add Column Names to the data frame 

```{r}
colnames(bridge) <- c("id","river","location","erected","purpose","length","lanes","clear","t_or_d", "material","span","rel_L","type")
head(bridge)
```
3. Change the abbreviation with full names
```{r}

bridge$river <- revalue(bridge$river,c("M"="Monongahela","O" = "Ohio", "A" = "Allegheny"))
bridge$length <- revalue(bridge$length, c("?" = "n/a"))
bridge$span <- revalue(bridge$span, c("?" = "n/a"))
bridge$lanes <- revalue(bridge$lanes, c("?" = "n/a"))
bridge$clear <- revalue(bridge$span, c("?" = "n/a"))
bridge$t_or_d <- revalue(bridge$t_or_d, c("?" = "n/a"))
bridge$material <- revalue(bridge$material, c("?" = "n/a"))
bridge$rel_L <- revalue(bridge$rel_L, c("?" = "n/a"))
head(bridge)
summary(bridge)

#bridge2[,6] <- revalue (bridge2[,6], c("?" = "n/a"))
#View ((bridge2[,6:11]))
#head(bridge2)
#View(bridge2)
```
Question: I tried searching simple way to do "Find and Replace" function in a whole data frame without resorting to using loop. 
Is there an easier way to do this?

4.Subsetting bridge over the Ohio river
```{r}
newbridge <- subset(bridge,river == "Ohio", select = c(id,river,purpose, length, material))
head(newbridge)
