---
title: "Project2"
author: "Angus Huang"
date: "October 11, 2015"
output: html_document
---
Project 2. Read 3 datasets and transform them from wide to long format and perform analysis.



```{r}
library (curl)
library (ggplot2)
library(tidyr)
library(dplyr)
setwd("C://users//angus//Documents//IS607//Project2")
```

#read in first dataset
```{r}
hr<- read.csv("C://users//angus//Documents//IS607//Project2//hr.csv")
```

#remove the extra subtotal
```{r}
hr2<-subset(hr,Role!='ALL')
hr2
```
#Read in second data set
```{r}
grade<-read.csv("C://users//angus//Documents//IS607//Project2//schoolgrade.csv")
grade
grade2 <-grade
```

#Correct the names of the vairables
```{r}
names(grade2)[5] <- "Social_Studies"
names(grade2)[7] <- "Days_Present"
grade2
```

#read the third long data set
```{r}
trade <- read.csv("C://users//angus//Documents//IS607//Project2//trade.csv")
trade2<- trade
```
#remove commas from numeric values and correct variables names
```{r}
trade2[,] <-lapply(trade2[,],function(trade2){gsub(",","",trade2)} )
trade2
names(trade2)[2] <- "Type"
names(trade2)[3:8] <- c("2013:e","2013:i","2014:e","2014:i","2015:e","2015:i")
```

#Convert wide from to long form and filled in the blank with correct data type
```{r}
trade3 <-trade2[2:13,]
trade3 <-trade3[complete.cases(trade3),]
#remove blank rows
trade3 <- trade3[!(is.na(trade3$`2015:i`) |trade3$`2015:i` ==""),]
trade3[2,1] <- "January"
trade3[4,1] <- "February"
trade3[6,1] <- "March"
trade3[8,1] <- "April"
head(trade3)
```
#gather data into tabular format, split the column data into separate column

```{r}
trade4 <- trade3 %>% gather (year,amount,3:8)
head(trade4)

trade4$tradecat<-sub(".*:","",trade4$year)
trade4$year <-sub(":.*","",trade4$year)
head(trade4)
```
#now spread the data & perform analysis.
Conclusion: The final table shows that American companies have strong export in service industry.  
```{r}
trade5 <-trade4%>% spread(tradecat,amount)
head(trade5)
trade5 <-trade5[order(trade5$Type),]
tbl_df(trade5)
trade5$e <- as.numeric(trade5$e)
trade5$i <- as.numeric(trade5$i)
trade5$exportratio <-(trade5$e/trade5$i)
trade5$exportratio <-(trade5$e/trade5$i)*100
names(trade5)[4:5]<-c("export","import")
trade5
```

#perform analysis on second dataset
```{r}
library(ggplot2)
hr2
hr3<-hr2[,1:3]
hr4<-hr3 %>%spread(Location,Current_HeadCount)
hr4$total <- hr4$DZ+hr4$GF+hr4$US
hr4
ggplot(data=hr4, aes(x=hr4$Role, y=hr4$total)) + geom_bar(stat="identity", position = "dodge")
```

#perform analysis on third dataset and perform correlation test between days present and average grade scores
```{r}
grade2
grade2$avg<-(grade2$English +grade2$Math+grade2$Science+grade2$Social_Studies+grade2$Technology)/5
grade2
cor(grade2$Days_Present, grade2$avg)
```


